The Astropy Project: Building an inclusive, open science project and status of the v2.0 software

### 2018-01-05 main.tex
rephrased parenthetical
doesn't -> does not (journals don't like such contractions?)

\texttt{Quantity} objects extend
\texttt{numpy.ndarray} objects and therefore
work well with many of the functions in \texttt{numpy} that support
array operations. For example, \texttt{Quantity} objects with angular
units can be directly passed in to the trigonometric functions implemented in
\texttt{numpy}. The units are internally converted to radians (what the \texttt{numpy}
trigonometric functions expect) before being passed to \texttt{numpy}.

@@

The typical user doesn't usually have to interact with the \texttt{Frame} or
\texttt{Representation} classes directly.
Instead, \texttt{astropy.coordinates} provides a high-level interface to
representing astronomical coordinates through the \texttt{SkyCoord} class,
which was designed to provide a single class that
accepts a wide range of possible inputs.
It supports coordinate data in any coordinate frame in any representation by
internally using the \texttt{Frame} and \texttt{Representation} classes.

>>>>

\texttt{Quantity} objects extend
\texttt{numpy.ndarray} objects and therefore
work well with many of the functions in \texttt{numpy} that support
array operations. For example, \texttt{Quantity} objects with angular
units can be directly passed in to the trigonometric functions implemented in
\texttt{numpy}. The units are internally converted to radians, which is what
the \texttt{numpy} trigonometric functions expect, before being passed to
\texttt{numpy}.

@@

The typical user does not usually have to interact with the \texttt{Frame} or
\texttt{Representation} classes directly.
Instead, \texttt{astropy.coordinates} provides a high-level interface to
representing astronomical coordinates through the \texttt{SkyCoord} class,
which was designed to provide a single class that
accepts a wide range of possible inputs.
It supports coordinate data in any coordinate frame in any representation by
internally using the \texttt{Frame} and \texttt{Representation} classes.
